---
output:
  html_document: default
  pdf_document:
    latex_engine: lualatex
---
<style type="text/css">
h2 {
border-left: 10px solid #3f75b3;
padding: 5px 5px 5px 10px;
background-color: #efefef;
}
</style>
---
title: "EESYS-DAE-M: Semester assignment 1"
subtitle: "Example solution"
author: Sebastian Günther
output: 
  html_document:
    theme: spacelab
    highlight: haddock
---
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '~/Downloads/')
library(dplyr)
```
# Example: Research Question from Tutorial
## Question to answer
*Does the attitude towards the environment (i.e., a higher score on environmentalism) translate into higher saving effects? (we assume it does)*

## Hypotheses
**H0**: Giving weight to environmentalism does not translate into stronger saving effects.

**H1**: Giving weight to environmentalism translates to stronger saving effects.

## Solution

1. Load Shower and Survey Data set
2. Transform the questions into numeric values. Calculate an environmentally friendly score per individual.
3. Calculate the average consumption during baseline and intervention phase per individual of the treatment group
4. Calculate savings for every individual (baseline - intervention)
5. Link the savings to the environmental score
6. Split the savings into two groups. Individuals with a low and a high environmentally friendly score.
7. Compare (one-sided t-test) means of savings of both groups.


```{r}
library(dplyr)
#Read the data
Shower_data <- read.csv2("~/Downloads/Shower_data.csv")
Survey_data <- read.csv2("~/Downloads/Shower_survey_data.csv")

transformValues <- function(x){
  x <- as.character(x)
  x <- ifelse(x=="Stimme nicht zu", -2, x)
  x <- ifelse(x=="Stimme eher nicht zu", -1, x)
  x <- ifelse(x=="Indifferent", 0, x)
  x <- ifelse(x=="Stimme eher zu", 1, x)
  x <- ifelse(x=="Stimme zu", 2, x)
  return(as.numeric(x))
}

Survey_data <- Survey_data  %>% dplyr::mutate_at(vars(starts_with("att")), funs(transformValues))

#Combine all the environmentalism scores into one (Note att1 and att8 are negative because the scale is flipped)
Survey_data <- Survey_data %>% dplyr::mutate(environmentalism = -att1+att2+att3+att4+att5+att6+att7-att8+att9+att10)

#Drop first shower
Shower_data <- Shower_data %>% dplyr::filter(Shower != 1) %>%
  dplyr::mutate(isTreatment = ifelse(group %in% c("1","2"), FALSE, TRUE),
                isIntervention = ifelse(Shower <= 10, FALSE, TRUE))

### Way1
#Calculate the water consumption for each phase and each group
treatmentShowers <- Shower_data %>% dplyr::filter(isTreatment) 

treatmentShowersBaseline <- treatmentShowers %>% dplyr::filter(!isIntervention) %>%
  dplyr::group_by(Hh_ID) %>%
  dplyr::summarise(baselineConsumption = mean(Volume))

treatmentShowersIntervention <- treatmentShowers %>% dplyr::filter(isIntervention) %>%
  dplyr::group_by(Hh_ID) %>%
  dplyr::summarise(interventionConsumption = mean(Volume))

#"Connect" both phases, introduce "savings"
consumptionPerPhase <- dplyr::inner_join(treatmentShowersBaseline, 
                                         treatmentShowersIntervention,
                                         by = "Hh_ID")

#Calculate the savings (simple approach, neglecting the control group, but ok for now)
VolumeSavings <- consumptionPerPhase %>% dplyr::mutate(savings = baselineConsumption - interventionConsumption)

#Join savings with survey data
VolumeSavingsEnriched <- dplyr::left_join(VolumeSavings, Survey_data, by = "Hh_ID")

#Create the group for the environmentally friendly people
VolumeSavingsEnrichedMedian <- VolumeSavingsEnriched %>% dplyr::mutate(environmentally_friendly = 
                                                                         environmentalism > median(Survey_data$environmentalism, na.rm = TRUE))

VolumeSavingsEnrichedMedian %>% dplyr::group_by(environmentally_friendly) %>%
  dplyr::summarise(meanSavings = mean(savings),
                   sdSavings = sd(savings))


# those who are environmentally friendly save less (according to the sample mean) than
# those who are not environmentally friendly. Strange at first sight.
# Apply the t-test - the result of the t-test is not surprising given the means
t.test(VolumeSavingsEnrichedMedian %>% dplyr::filter(environmentally_friendly) %>% dplyr::pull(savings),
       VolumeSavingsEnrichedMedian %>% dplyr::filter(!environmentally_friendly) %>% dplyr::pull(savings), 
       alternative="greater")
```
## Result
**We fail to reject H0.**  

The t-tests suggests that people who are environmentally friendly use as much water than those who are not environmentally friendly.